Analysis of Bauer et al. (unpublished) Field experiment: <br> Favourable Conservation Status (FCS)

### 2022-12-09 R/model_fcs_check.Rmd
Update model_fcs_check.Rmd

Analysis motivated by Applestein et al. (2021) Restor Ecol [DOI: 10.1111/rec.13596](https://doi.org/10.1111/rec.13596)

@@

```{r bayes-factor}
brms::bayes_factor(m_1, m_2)
```

@@

```{r effect-sizes}
emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |
          survey_year_fct, type = "response")
```

>>>>

Bayesian analysis motivated by Applestein et al. (2021) Restor Ecol [DOI: 10.1111/rec.13596](https://doi.org/10.1111/rec.13596)

@@

```{r bayes-factor-1, results = FALSE}
bayes_factor <- brms::bayes_factor(m_1, m_2)
```

```{r bayes-factor-2}
bayes_factor
```

@@

```{r effect-sizes}
draws1
emmeans(m_1, revpairwise ~ target_type + sand_ratio | exposition |
          survey_year_fct, type = "response")
```
